FireSim2019_ManuscriptFigures

### 2023-03-16 Manuscript-figures.Rmd

#library(knitr)
library(ggplot2)
#library(plyr)
library(dplyr)
library(tidyr)
#library(car) # For Levene's Test
library(phyloseq)
#library(scatterplot3d)
#library(ggtree)
library(cowplot) # add-on to ggplot to assist in publication-quality figs
#library(qwraps2)
library(vegan)
library(tidyverse)
#library(psych) # scatterplot matrix (pairs, or pairs.panels)
library(ggtern) # for ternary plots
#library(devtools)
#library(DivNet)
#library(breakaway) # for richness estimates

@@

# Load phyloseq objects
```{r, message = FALSE}
#df.pb.gDNA.OTU <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/df.pb.gDNA.norm.csv')
#df.pb.cDNA.OTU <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/df.pb.cDNA.norm.csv')
#df.SI.OTU <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/df.SI.norm.csv')
#df.LI.norm <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/df.LI.norm.csv')

# Starting phyloseq:
### Normalized + tree
ps.norm.full <- readRDS('../../data/sequence-data/LibCombined/phyloseq-objects/ps.norm.full')
ps.norm.full <- prune_taxa(taxa_sums(ps.norm.full)>0, ps.norm.full)

@@

#ps.raw.pb <- prune_samples(sample_data(ps.raw.full)$incub.trtmt == 'pb', ps.raw.full)
#ps.norm.pb <- prune_samples(sample_data(ps.norm.full)$incub.trtmt == 'pb', ps.norm.full)

# ps.norm.pb
#ps.norm.pb.gDNA <- prune_samples(sample_data(ps.norm.gDNA)$incub.trtmt == 'pb',ps.norm.gDNA)
#ps.norm.pb.cDNA <- prune_samples(sample_data(ps.norm.cDNA)$incub.trtmt == 'pb',ps.norm.cDNA)
# ps.norm.SI
#ps.norm.SI <- prune_samples(sample_data(ps.norm.gDNA)$incub.trtmt == 'SI',ps.norm.gDNA)
# ps.norm.LIwA
#ps.norm.LIwA <- prune_samples(sample_data(ps.norm.gDNA)$incub.trtmt == 'LIwA',ps.norm.gDNA)
#ps.norm.LIn <- prune_samples(sample_data(ps.norm.gDNA)$incub.trtmt == 'LIn',ps.norm.gDNA)
#ps.norm.LI <- prune_samples(sample_data(ps.norm.gDNA)$incub.trtmt %in% c('LIn', 'LIwA'),ps.norm.gDNA)
#ps.raw.LI <- prune_samples(sample_data(ps.raw.gDNA)$incub.trtmt %in% c('LIn', 'LIwA'),ps.raw.gDNA)

#ps.norm.SI<- prune_taxa(taxa_sums(ps.norm.SI)>0, ps.norm.SI)
```

# Figure 2 (burn temperature, pH and C:N change, respiration coefficients):
```{r}
# Temperatures ----
df.Temp <-read.csv('../../data/burn-thermocouple-temp-logs/Temp-all-burns-clean.csv')
df.Temp$Thermo_position <- factor(df.Temp$Thermo_position, levels = c('Mid','Low'))

@@

# pH and C:N change ----
pChange_pH <- ggplot(subset(df.meta, incub.trtmt == 'SI')) + 
  geom_boxplot(aes(x=horizon, y = pH, fill = burn.trtmt), varwidth = FALSE) + 
    theme_bw()+
  labs(x= 'Soil horizon',
     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
       y = 'Soil pH',
       fill = 'Burn treatment') + 
  scale_fill_manual(values = c('grey50','orange','red'),
                     limits = c('control','wet','dry'),
                     labels = c('Unburned\ncontrol','Moist soil\nburn','Dry soil\nburn')) +
  scale_x_discrete(limits = c('O','A'),
                     labels = c('Organic','Mineral')) +
  #scale_fill_manual(values = c("deepskyblue3","saddlebrown"),
  # scale_fill_manual(values = c("slateblue4","palegreen3"),
  # #scale_fill_manual(values = c("darkgreen","saddlebrown"),
  #                    limits = c('O','A'),
  #                    labels = c('Organic','Mineral')) +
  # scale_x_discrete(limits = c('control','wet','dry'),
  #                    labels = c('Unburned\ncontrol','Wet soil\nburn','Dry soil\nburn')) +
  theme(axis.text.y = element_text(size = 14),
        legend.title = element_text(size=14),
        axis.text.x = element_text(size = 14),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
        strip.text = element_text(size=14),
        legend.text = element_text(size=14),
        legend.position = '',
       # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical")

@@

# Respiration coefficients ----
#   Decay model coefficients at end of 5 week incubation (Days=34)
#   after adjusting for total C
df.coefs <- read.csv('../../data/2-pool-decay-model-output-SI-adjusted-for-total-C.csv') %>%
  subset(t==34) 
# df.coefs <- read.csv('../../data/2-pool-decay-model-output-LIwA-adjusted-for-total-C.csv') %>%
#   subset(t==180)

@@

# Figure 3: RNA and DNA concentration (ng/g soil)
```{r}
df <- read.csv('../../data/raw-data/pb-RNA-and-DNA-conc.csv')

@@

@@

# Figure 4 - weighted mean gene copy number
Which bacteria are fast-growing following burn treatments of varying severity and under a range of moisture conditions?
```{r}
df.WMCN.pb <- read.csv('../../data/WtMeanCopyNum_pb_gDNA.csv')
df.WMCN.SI <- read.csv('../../data/WtMeanCopyNum_SI.csv')
df.WMCN.LIwA <- read.csv('../../data/WtMeanCopyNum_LIwA.csv')

@@

# Figure 5 - Calculate bray-curtis dissimilarity for autoclaving
```{r, message = FALSE}
df.distances <- read.csv('../../data/bray-curtis-dissimilarites.csv')

test = lm(BC.distance.btw.burned.and.control~change.pH, data=subset(df.distances, incub.trtmt == 'LIwA' & horizon == 'A' & burn.trtmt == 'dry'))

test
summary(test)

# Hrzn.degree.hrs vs. Bray-Curtis dissimilarities for -pb RNA and DNA -----
p = ggplot(subset(df.meta.combined, burn.trtmt =='dry' & 
                    incub.trtmt == 'pb'),
           aes(x=hrzn.degree.hrs, y = BC.distance.btw.burned.and.control,fill = horizon)) +
  geom_point(shape='circle filled',
             stroke=1,
             alpha = 0.8,
             size=3) +
  theme_bw() +
  facet_grid(DNA.type~horizon, scales = 'free',
             labeller = labeller(incub.trtmt = IncubLabels,
                                 burn.trtmt = BurnLabels, 
                                 DNA.type = DNALabels)) + 
  labs(y = 'Bray-Curtis dissimilarity compared to control', 
       title = 'Bray-Curtis dissimilarities') + 
  scale_fill_manual(values = c('black','grey70'),
                     limits = c('O','A'),
                     labels = c('Organic','Mineral')) +
  theme(axis.title = element_text(size=12),
        axis.text = element_text(size=12),
        legend.title = element_text(size=12),
        legend.text = element_text(size=12)) + 
    stat_smooth(method=lm,se = FALSE,color='black')

# Stats -----
test <- aov(BC.distance.btw.burned.and.control ~ hrzn.degree.hrs, 
            data = subset(df.meta.combined,incub.trtmt == 'pb' & DNA.type == 'cDNA' &burn.trtmt == 'wet'))
summary(test) 
```

# Responders as fraction of total reads
```{r}
df <- read.csv('../../data/sequence-data/LibCombined/corncob-output/Manuscript/Trait-responder-OTUs.csv')

# Table summarize composition of responders by phylum:
df.phylum <- subset(df, select = c(mu.survival.max, mu.fast.max, mu.affinity.max, Phylum)) %>% unique()

df.phylum %>% mutate(Phylum = as.factor(Phylum)) %>% subset(mu.affinity.max>0) %>%subset(select = c(Phylum)) %>% View()

df.Class <- subset(df, select = c(mu.survival.max, mu.fast.max, mu.affinity.max, Class)) %>% unique()

df.Class %>% mutate(Class = as.factor(Class)) %>% subset(mu.fast.max>0) %>%subset(select = c(Class)) %>% summary()

# Count number of taxa by sample:
# Create a factor corresponding to the Genera
genfac = factor(tax_table(ps.norm.cDNA)[, "Genus"])
# Tabulate the counts for each genera in each sample
gentab = apply(otu_table(ps.norm.cDNA), MARGIN = 2, function(x) {
    tapply(x, INDEX = genfac, FUN = sum, na.rm = TRUE, simplify = TRUE)
})
head(gentab)[, 1:10]

x <- as.data.frame(gentab)
```

# New figures: 
```{r}
### BC dissim of burned vs. unburned on the x axis with a respiration metric on the y axis

# Import BC dissimilarity data
df.distances <- read.csv('../../data/bray-curtis-dissimilarites.csv')

# Combine this with metadata
df.distances <- merge(df.distances, subset(df.meta, burn.trtmt != 'control'))

# Organize
df.distances$incub.trtmt <- factor(df.distances$incub.trtmt, levels = c('pb','SI','LIwA','LIn'))
df.distances$horizon <- factor(df.distances$horizon, levels = c('O','A'))

# Import respiration data:
df.resp <- read.csv("../../data/fractional-c-remaining.csv")

df.merge <- merge(df.distances, df.resp, by = c('core.id','incub.trtmt')) %>%
  subset(incub.trtmt == 'SI') %>%
  subset(DayFactor == 34) %>%
  mutate(mass.C.respired = mass.C.remaining.g * (1-fractional.C.remaining))

pBC = ggplot(df.merge, aes(x=BC.distance.btw.burned.and.control, y=k1, color = horizon)) + 
  geom_point() + 
  scale_color_manual(values = c('darkgreen','grey70'))+
  stat_smooth(method=lm,se = FALSE,color='black') +
  theme_bw() + 
  #facet_wrap(~horizon, ncol=2,scales = 'fixed',
   #          labeller = labeller(horizon = HorizonLabels))+
  labs(y = 'Decay rate constant for \nfast C pool (k1)',
       x = 'Bray-Curtis dissimilarity \ncompared to unburned control')

summary(lm(data=df.merge,k1~BC.distance.btw.burned.and.control))

### Ordination colored by respiration metric:
# Full ordination
ps.norm.SI <- prune_samples(sample_data(ps.norm.full)$incub.trtmt =='SI', ps.norm.full)
ps.norm.SI <- prune_taxa(taxa_sums(ps.norm.SI)>0, ps.norm.SI)

ord.nmds = ordinate(ps.norm.SI,method = "NMDS",ddistance="wunifrac",k=3, weighted=TRUE)

# quick look at results:
plot_ordination(ps.norm.SI,ord.nmds,color="burn.trtmt",shape="incub.trtmt")
colnames(sample_data(ps.norm))

# Ordination plot with horizons and deg.hrs
p1 = plot_ordination(ps.norm.SI, ord.nmds, axes = c(1,2), color = "",
                      shape = 'burn.trtmt') + 
  #facet_grid(~horizon, labeller = labeller(horizon = HorizonLabels))+
  geom_point(size=3, alpha=0.8) +
  # scale_color_gradientn(colours = c('gold2','red','red4','black')) +
  # scale_color_manual(values = c('black','orange','red'),
  #                    labels = c('Unburned control', 'Wet soil burn','Wry soil burn'),
  #                    breaks = c('control','wet','dry'))+
  scale_shape_manual(values = c('circle','square','triangle'),
                     labels = c('Unburned control', 'Moist soil','Dry soil'),
                     breaks = c('control','wet','dry')) +
  #scale_shape_discrete(labels = c('Picea' = 'Picea spp.', 'Populus_tremuloides' = 'Populus tremuloides','Pinus_banksiana' = 'Pinus banksiana')) +
  #scale_shape_manual(values = c('circle','triangle'),
   #                  labels = c('O horizon','Mineral'),
    #                 breaks = c('O','A')) + 
  theme(legend.text = element_text(size = 12),
        axis.title = element_text(size=12),
        axis.text = element_text(size=12),
        legend.title = element_text(size=12)) + 
  labs(shape = 'Burn treatment',
       color = 'Fractional size\nof fast C pool') +
  theme_bw()

## What fraction of total reads in dry soil burns 24 hr post burn were bacillus?
#  Bacillus fire surviving taxa = 8f0e2646c1389192d5a822f62bd295cf, 8adb5559e135233565acfea1287280bf
df <- read.csv('../../data/sequence-data/LibCombined/corncob-output/Manuscript/Trait-responder-OTUs.csv')

df.bac <- read.csv('../../data/sequence-data/LibCombined/corncob-output/Manuscript/Trait-responder-OTUs.csv') %>%
  subset(mu.survival.max>0) %>%
  subset(Genus=='Bacillus')

ps.norm.bac <- prune_samples(sample_data(ps.norm.gDNA)$incub.trtmt == 'pb', ps.norm.gDNA) 
ps.norm.bac <- prune_taxa(taxa_names(ps.norm.bac) %in% df.bac$OTU, ps.norm.bac)

bac <- psmelt(ps.norm.bac)
# Answer 9% (8f0e2646c1389192d5a822f62bd295cf) and 4% (8adb5559e135233565acfea1287280bf) of total reads in dry soil burns

### What percentage of all OTUs were identified as fast growers?
df.fast <- df %>%
  subset(mu.fast.max>0)

ps.norm.SI <- prune_samples(sample_data(ps.norm.gDNA)$incub.trtmt == 'SI', ps.norm.gDNA) 
ps.norm.SI <- prune_taxa(taxa_sums(ps.norm.SI)>0, ps.norm.SI)
ps.norm.SI
# Answer: IN the 5 week incubation, 0.4%

### Max relative abundance of responding taxa in lab samples?
ps.responders <- prune_taxa(taxa_names(ps.norm.gDNA) %in% df$OTU, ps.norm.gDNA)
df.responders <- psmelt(ps.responders)

df.responders <- df.responders %>%
  subset(select = c(Sample, Abundance, Full.id,burn.trtmt))

Num.responders <- df.responders %>% group_by(Full.id) %>% mutate(abun = sum(Abundance))
max(Num.responders$abun) # = 0.604

Num.responders.in.dry <- df.responders %>%
  subset(burn.trtmt == 'dry') %>% 
  group_by(Full.id) %>% 
  mutate(combined.abun = sum(Abundance))

mean(Num.responders.in.dry$combined.abun) # = 15
sd(Num.responders.in.dry$combined.abun) # =

# Figure 6: Trade offs
```{r}

df <- read.csv('../../data/sequence-data/LibCombined/corncob-output/Manuscript/all-responders.csv')
df.L2FC <- read.csv('../../data/sequence-data/LibCombined/corncob-output/Full_L2FC.csv')

# Checking to make sure that L2FC calculations didn't drop any OTUs. 
df.survival <- df %>%
  subset(experiment == 'survival'&
           T.cutoff %in% c('Low thermo > 50C','Mid thermo > 50C') & 
           intercept > 0) %>%
  subset(intercept > (mean(intercept)-1*sd(intercept)) ) %>% 
  subset(select = c(OTU,Phylum, Class, Order, Family, Genus, Species)) %>%
  unique()

df.survival.L2FC <- df.L2FC %>%
  subset(experiment == 'survival'  &
           T.cutoff %in% c('low thermo > 50C','Mid thermo > 50C') &
           mu > 0) %>%
  subset(mu > (mean(mu)-1*sd(mu))) %>%
  subset(select = c(OTU)) %>%
  unique()

df.survival.merge <- merge(df.survival, df.survival.L2FC)
#write.csv(df.survival,'../tables/survivors.csv', row.names=FALSE)

dim(df.survival)
dim(df.survival.L2FC)

df.fast <- df %>%
  subset(experiment == 'fast growth'&
           intercept > 0) %>%
  subset(intercept > (mean(intercept)-1*sd(intercept)) ) %>% 
  subset(select = c(OTU,Phylum, Class, Order, Family, Genus, Species)) %>%
  unique()
dim(df.fast)

df.fast.L2FC  <- df.L2FC %>%
  subset(experiment == 'fast growth'  &
           mu > 0) %>%
  subset(mu > (mean(mu)-1*sd(mu))) %>%
  subset(select = c(OTU)) %>%
  unique() 
dim(df.fast.L2FC)
df.fast.merge <- merge(df.fast.L2FC, df.fast)

df.affinity <- df %>%
  subset(experiment == 'affinity'&
           T.cutoff %in% c('Low thermo > 50','Mid thermo > 50') &
           intercept > 0) %>%
  subset(intercept > (mean(intercept)-1*sd(intercept)) ) %>% 
  subset(select = c(OTU,Phylum, Class, Order, Family, Genus, Species)) %>%
  unique()
dim(df.affinity)

df.affinity.L2FC  <- df.L2FC %>%
  subset(experiment == 'affinity'  &
           T.cutoff %in% c('low thermo > 50 C','mid thermo > 50 C') &
           mu > 0) %>%
  subset(mu > (mean(mu)-1*sd(mu))) %>%
  subset(select = c(OTU)) %>%
  unique() 
dim(df.affinity.L2FC)

df.affinity.merge <- merge(df.affinity.L2FC, df.affinity)

df.full <- df.L2FC

# Filter u ----
# First pull out enriched taxa:
df <-  subset(df.full, mu > 0)

# Create a dataframe for survivors filtering by temperature cutof and 1 sd from 
#   the mean of the intercept. Remove duplicate taxa. 
df.survival <- subset(df, experiment == 'survival' &
                        T.cutoff %in% c('low thermo > 50 C','mid thermo > 50 C')) %>%
  subset(mu > (mean(mu)-1*sd(mu))) %>%
  mutate(survival.L2FC = L2FC) %>%
  dplyr::group_by(OTU) %>%
  dplyr::mutate(max.mu = max(mu)) %>%
  subset(mu == max.mu) %>%
  subset(select = c(OTU, survival.L2FC)) %>%
  unique()%>%
  mutate(survivor = 'yes')

# Create dataframe for fast growers filtering for 1 sd from the mean: -----
df.fast <- subset(df, experiment == 'fast growth') %>%
  subset(mu > (mean(mu)-1*sd(mu))) %>%
  mutate(fast.L2FC = L2FC)%>%
  dplyr::group_by(OTU) %>%
  dplyr::mutate(max.mu = max(mu)) %>%
  subset(mu == max.mu) %>%
  subset(select = c(OTU, fast.L2FC)) %>%
  unique() %>%
  mutate(fast = 'yes')

# Create data frame for affinity taxa filtering for temperature cutoff and 1
#   sd from the mean:
df.affinity <- subset(df, experiment == 'affinity' &
                        T.cutoff %in% c('Low thermo > 50C','Mid thermo > 50C')) %>%
  subset(mu > (mean(mu)-1*sd(mu))) %>%
  mutate(affinity.L2FC = L2FC)%>%
  dplyr::group_by(OTU) %>%
  dplyr::mutate(max.mu = max(mu)) %>%
  subset(mu == max.mu) %>%
  subset(select = c(OTU, affinity.L2FC)) %>%
  unique()%>%
  mutate(affinity = 'yes')

# Combine the three dataframes:
df.index <- merge(df.survival, df.fast, all = TRUE) %>%
  merge(df.affinity, all = TRUE) %>%
  subset(select = c(OTU, survivor, fast, affinity))

df.ids <- read.csv('../data/sequence-data/LibCombined/corncob-output/all-responders.csv') %>%
  subset(select = c(OTU, Domain, Phylum, Class, Order, Family, Genus, Species)) %>%
  unique()
df.ids <- merge(df.index,df.ids, all = FALSE)
write.csv(df.ids, '../tables/all-responding-otus.csv', row.names = FALSE)

# Next take the full responder dataset and filter out any duplicate taxa

x.1 <- df.full %>%
  subset(experiment == 'survival') %>%
  subset(select = c(OTU, mu, experiment,horizon,
                    fold.change, L2FC)) %>%
  dplyr::group_by(OTU, experiment) %>%
  dplyr::mutate(max.mu = max(abs(mu))) %>%
  subset(max.mu == abs(mu)) %>%
  dplyr::mutate(survival.L2FC = L2FC) %>%
  subset(select = c(OTU, survival.L2FC)) %>%
  unique()

x.2 <- df.full %>%
  subset(experiment == 'fast growth') %>%
  subset(select = c(OTU, mu, experiment,horizon,
                    fold.change, L2FC)) %>%
  dplyr::group_by(OTU, experiment) %>%
  dplyr::mutate(max.mu = max(abs(mu))) %>%
  subset(max.mu == abs(mu)) %>%
  dplyr::mutate(fast.L2FC = L2FC) %>%
  subset(select = c(OTU, fast.L2FC)) %>%
  unique()

x.3 <- df.full %>%
  subset(experiment == 'affinity') %>%
  subset(select = c(OTU, mu, experiment,horizon,
                    fold.change, L2FC)) %>%
  dplyr::group_by(OTU, experiment) %>%
  dplyr::mutate(max.mu = max(abs(mu))) %>%
  subset(max.mu == abs(mu)) %>%
  dplyr::mutate(affinity.L2FC = L2FC) %>%
  subset(select = c(OTU, affinity.L2FC)) %>%
  unique()

x <- merge(x.1, x.2, all = TRUE) %>%
  merge(x.3, all = TRUE)

# Create list of responding taxa:
responding.OTU.list = unique(df.index$OTU)

# Then filter this to include only taxa identified as responders (i.e. meeting
#   the respective cutoffs for at least one of the three trait experiments)
df.traits <- filter(x, OTU %in% responding.OTU.list) %>% 
  unique()

df.traits <- merge(df.index, df.traits)

#df.traits <- test %>%
#  merge(unique(subset(df, select = c(OTU, Domain, Phylum, Class, Order, Family, Genus, Species))))

df.traits$trait = 'null'

for (i in 1:nrow(df.traits)) {
  if (df.traits$survivor[i] == 'yes' &
      df.traits$survival.L2FC[i] > 0 &
      is.na(df.traits$fast[i]) == TRUE &
      is.na(df.traits$affinity[i]) == TRUE) {
    df.traits$trait[i] = 'survival'
      } else if (df.traits$fast[i] == 'yes' &
                 df.traits$fast.L2FC[i] > 0 &
                 is.na(df.traits$survivor[i]) == TRUE &
                 is.na(df.traits$affinity[i]) == TRUE) {
        df.traits$trait[i] = 'fast growth'
      } else if (df.traits$affinity[i] == 'yes' &
                 df.traits$affinity.L2FC[i] > 0 &
                 is.na(df.traits$survivor[i]) == TRUE &
                 is.na(df.traits$fast[i]) == TRUE) {
        df.traits$trait[i] = 'affinity'
      } else if (df.traits$survivor[i] == 'yes' &
                 df.traits$survival.L2FC[i] > 0 &
                 df.traits$fast[i] == 'yes' &
                 df.traits$fast.L2FC[i] > 0 &
                 is.na(df.traits$affinity[i]) == TRUE) {
        df.traits$trait[i] = 'survival and fast growth'
      } else if (df.traits$fast[i] == 'yes' &
                 df.traits$fast.L2FC[i] > 0 &
                 df.traits$affinity[i] == 'yes' &
                 df.traits$affinity.L2FC[i] > 0 &
                 is.na(df.traits$survivor[i]) == TRUE) {
        df.traits$trait[i] = 'fast growth and affinity'
      } else if (df.traits$survivor[i] == 'yes' &
                 df.traits$survival.L2FC[i] > 0 &
                 df.traits$affinity[i] == 'yes' &
                 df.traits$affinity.L2FC[i] > 0 &
                 is.na(df.traits$fast[i]) == TRUE) {
        df.traits$trait[i] = 'survival and affinity'
      } else if (df.traits$survivor[i] == 'yes' &
                 df.traits$survival.L2FC[i] > 0 &
                 df.traits$fast[i] == 'yes' &
                 df.traits$fast.L2FC[i] > 0 &
                 df.traits$affinity[i] == 'yes' &
                 df.traits$affinity.L2FC[i] > 0) {
        df.traits$trait[i] = 'survival, fast growth, \nand affinity'
      } else {
        df.traits$trait[i] = 'none'
      } 
}

unique(df.traits$trait)

head(df.traits)

library(RColorBrewer)
old.trait.colors = c('gold','green','royalblue3','purple','darkred','orange','black')
trait.colors = c(brewer.pal(n=10, name = 'Spectral'), 'black')

trait.colors = c('#E6AB02','#33A02C','#386CB0','#762A83','#D73027','#F46D43','black')

# Finally build trait trade-off plots:
p1 = ggplot(df.traits) + 
  geom_hline(yintercept = 0) + 
  geom_vline(xintercept = 0)+ 
  geom_point(aes(x=survival.L2FC, y=fast.L2FC, color = trait, fill = trait), shape = 21,size=4, alpha=1) + 
  theme_bw() +
  labs(x= expression(Survival~(log[2]-fold~change)),
       #  y = 'Decay rate constant for fast C pool \nlog(k1)',
       y = expression(Fast~growth~(log[2]-fold~change))) + 
  scale_color_manual(limits = c('survival','survival and fast growth','fast growth','fast growth and affinity',
                                'affinity','affinity and survival','survival, fast growth, \nand affinity'),
                     values = trait.colors) + 
  scale_fill_manual(limits = c('survival','survival and fast growth','fast growth','fast growth and affinity',
                                'affinity','affinity and survival','survival, fast growth, \nand affinity'),
                     values = trait.colors) + 
  theme(axis.text.y = element_text(size = 14),
        legend.title = element_text(size=10),
        axis.text.x = element_text(size = 14),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
        strip.text = element_text(size=14),
        legend.text = element_text(size=10),
        legend.position = 'none',
        # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical")+
  stat_smooth(aes(x=survival.L2FC, y=fast.L2FC),method=lm, se=FALSE, color = 'grey40',
              geom = 'smooth')

p2 = ggplot(df.traits) + 
  geom_hline(yintercept = 0) + 
  geom_vline(xintercept = 0)+ 
  geom_point(aes(x=fast.L2FC, y=affinity.L2FC, color = trait, fill=trait), shape = 21,  size=4,alpha=1) + 
  theme_bw() +
  labs(x= expression(Fast~growth~(log[2]-fold~change)),
       #  y = 'Decay rate constant for fast C pool \nlog(k1)',
       y = expression(Post~fire~envir.~affinity~(log[2]-fold~change))) + 
  scale_color_manual(limits = c('survival','survival and fast growth','fast growth','fast growth and affinity',
                                'affinity','affinity and survival','survival, fast growth, \nand affinity'),
                     values = trait.colors) + 
  scale_fill_manual(limits = c('survival','survival and fast growth','fast growth','fast growth and affinity',
                                'affinity','affinity and survival','survival, fast growth, \nand affinity'),
                     values = trait.colors) + 
  theme(axis.text.y = element_text(size = 14),
        legend.title = element_text(size=10),
        axis.text.x = element_text(size = 14),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
        strip.text = element_text(size=14),
        legend.text = element_text(size=10),
        legend.position = 'none',
        # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical")

p3 = ggplot(df.traits) + 
  geom_hline(yintercept = 0) + 
  geom_vline(xintercept = 0)+ 
  geom_point(aes(x=affinity.L2FC, y=survival.L2FC, color = trait, fill = trait), 
             shape = 21,size=4,alpha=1) + 
  theme_bw() +
  labs(x=expression(Post~fire~envir.~affinity~(log[2]-fold~change)),
       #  y = 'Decay rate constant for fast C pool \nlog(k1)',
       y = expression(Survival~(log[2]-fold~change)),
       color = 'Bacterial strategy:',
       fill = 'Bacterial strategy:') + 
  scale_color_manual(limits = c('survival','survival and fast growth','fast growth','fast growth and affinity',
                                'affinity','affinity and survival','survival, fast growth, \nand affinity'),
                     values = trait.colors) + 
  scale_fill_manual(limits = c('survival','survival and fast growth','fast growth','fast growth and affinity',
                                'affinity','affinity and survival','survival, fast growth, \nand affinity'),
                     values = trait.colors) + 
  theme(axis.text.y = element_text(size = 14),
        legend.title = element_text(size=14),
        axis.text.x = element_text(size = 14),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
        strip.text = element_text(size=14),
        legend.text = element_text(size=14),
        legend.position = 'none',
        # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical")
cowplot::plot_grid(p1, p2,p3, ncol=3)

test <- lm(fast.L2FC ~ affinity.L2FC, data = df.traits)
summary(test)
test
#

x <- grDevices::rainbow(n=6)

df <- read.csv('../data/sequence-data/LibCombined/corncob-output/all-responders.csv')
df <- subset(df, select = c(OTU, Domain, Phylum, Class, Order, Family, Genus, Species)) %>%
  unique()

df.traits <- merge(df.traits,df)
dim(df.traits)
```

>>>>

library(ggplot2)
library(dplyr)
library(tidyr)
library(phyloseq)
library(cowplot) 
library(vegan)
library(tidyverse)

@@

# Load phyloseq objects
```{r, message = FALSE}
# Starting phyloseq:
### Normalized + tree
ps.norm.full <- readRDS('../../data/sequence-data/LibCombined/phyloseq-objects/ps.norm.full')
ps.norm.full <- prune_taxa(taxa_sums(ps.norm.full)>0, ps.norm.full)

@@

# Figure 2A-C (burn temperature, pH and C:N change, respiration coefficients):
```{r}
# Temperature, Fig. 2A ----
df.Temp <-read.csv('../../data/burn-thermocouple-temp-logs/Temp-all-burns-clean.csv')
df.Temp$Thermo_position <- factor(df.Temp$Thermo_position, levels = c('Mid','Low'))

@@

# pH and C:N change, Fig. 2B ----
pChange_pH <- ggplot(subset(df.meta, incub.trtmt == 'SI')) + 
  geom_boxplot(aes(x=horizon, y = pH, fill = burn.trtmt), varwidth = FALSE) + 
    theme_bw()+
  labs(x= 'Soil horizon',
     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
       y = 'Soil pH',
       fill = 'Burn treatment') + 
  scale_fill_manual(values = c('grey50','orange','red'),
                     limits = c('control','wet','dry'),
                     labels = c('Unburned\ncontrol','Moist soil\nburn','Dry soil\nburn')) +
  scale_x_discrete(limits = c('O','A'),
                     labels = c('Organic','Mineral')) +
  #scale_fill_manual(values = c("deepskyblue3","saddlebrown"),
  # scale_fill_manual(values = c("slateblue4","palegreen3"),
  # #scale_fill_manual(values = c("darkgreen","saddlebrown"),
  #                    limits = c('O','A'),
  #                    labels = c('Organic','Mineral')) +
  # scale_x_discrete(limits = c('control','wet','dry'),
  #                    labels = c('Unburned\ncontrol','Wet soil\nburn','Dry soil\nburn')) +
  theme(axis.text.y = element_text(size = 14),
        legend.title = element_text(size=14),
        axis.text.x = element_text(size = 14),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
        strip.text = element_text(size=14),
        legend.text = element_text(size=14),
        legend.position = '',
       # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical")

@@

# Respiration coefficients, Fig. 2C ----
#   Decay model coefficients at end of 5 week incubation (Days=34)
#   after adjusting for total C
df.coefs <- read.csv('../../data/2-pool-decay-model-output-SI-adjusted-for-total-C.csv') %>%
  subset(t==34) 
# df.coefs <- read.csv('../../data/2-pool-decay-model-output-LIwA-adjusted-for-total-C.csv') %>%
#   subset(t==180)

@@

# Figure 2D: RNA and DNA concentration (ng/g soil)
```{r}
df <- read.csv('../../data/raw-data/pb-RNA-and-DNA-conc.csv')

@@

# Lab and field ordination, Figure 3 -----
See "Merged_paper_figures_Revision_Github.R" script

# Trait abundance in field data, Figure 4: ----
See "Merged_paper_figures_Revision_GitHub.R" script

# Rel abundance adjusted by copy num, Figure 5 -----
See "Merged_paper_figures_Revision_GitHub.R" script

# Total trait abun by BC dissimilarity, Figure 6 -----
See "Merged_paper_figures_Revision_GitHub.R" script

# Supplementary
```{r}
# Carbon and nitrogen loss, Figure S2 -----
pChange_C <- ggplot(subset(df.meta, incub.trtmt == 'SI')) + 
  geom_boxplot(aes(x=burn.trtmt, y = percent.total.C, fill = horizon), alpha = 0.7, varwidth = FALSE) + 
    theme_bw()+
  labs(x= 'Burn treatment',
     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
       y = 'Total C (%)',
       fill = 'Soil horizon') + 
  scale_fill_manual(values = c('black','grey90'),
                     limits = c('O','A'),
                     labels = c('Organic','Mineral')) +
  scale_x_discrete(limits = c('control','wet','dry'),
                     labels = c('Unburned\ncontrol','Wet soil\nburn','Dry soil\nburn')) +
  theme(axis.text.y = element_text(size = 14),
        legend.title = element_text(size=14),
        axis.text.x = element_text(size = 14),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
        strip.text = element_text(size=14),
        legend.text = element_text(size=14),
        legend.position = '',
       # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical")

# C remaining as fraction of total, Figure S3, S4 -----
#   See incubations_microbial_respiration.R
# Full ordination, Fig. S6 ----
ps.full.dataset <-readRDS('../../../CombinedFireSim1519/ps.1519FireSim.merged')
tree <- ape::read.tree('../../../CombinedFireSim1519/tree/merged-exported-tree/tree.nwk')

# BC dissimilarity and pH change, Figure S7-----
df.distances <- read.csv('../../data/bray-curtis-dissimilarites.csv')

# Respiration rate figures, S8, S9, S10-----
#   See "incubations_microbial_respiration.R" script

# Traits as fraction of total reads in lab data, Figure S11-----
df <- read.csv('../../data/sequence-data/LibCombined/corncob-output/Manuscript/Trait-responder-OTUs.csv')

# PERMANOVAs, Supplementary:
```{r}
ps.E1 <- prune_samples(sample_data(ps.norm.full)$incub.trtmt == 'pb' &
                         sample_data(ps.norm.full)$DNA.type == 'cDNA', ps.norm.full)
ps.E1 <- prune_taxa(taxa_sums(ps.E1)>0, ps.E1)
ps.E1

@@

# Weighted mean gene copy number
Which bacteria are fast-growing following burn treatments of varying severity and under a range of moisture conditions?
```{r}
df.WMCN.pb <- read.csv('../../data/WtMeanCopyNum_pb_gDNA.csv')
df.WMCN.SI <- read.csv('../../data/WtMeanCopyNum_SI.csv')
df.WMCN.LIwA <- read.csv('../../data/WtMeanCopyNum_LIwA.csv')

@@
